IRTF Spectro-Photometry of Two Rotating Brown Dwarfs: \\2MASS J08354256-0819237 and 2MASS J18212815+1414010

### 2016-11-15 ms.tex
I mainly touched up the intro and added a reference to Ben Lew's paper.

The cloud layers may be studied from the direct spectroscopy of a populations of brown dwarf atmospheres \citep[e.g.][]{burgasser2006ltTrans,liu2006}.
Brown dwarfs may be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time \citep[e.g.][]{yang2016exStormsBD}.
In the case where the targets are bright enough, Doppler imaging can be used to map out the cloud structures on brown dwarfs as in \citet{crossfield2014dopplerimg}.

The photometry brown dwarfs at the L/T transition is explained by (silicate and sulfide?) clouds at a temperature of (?).

@@

We observed the two brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres.
2MASS J18212815+1414010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
The spectral type is peculiar and has also been designated as L4 \citep{gagne2015banyan7}.
2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L5 brown dwarf known to be variable with a period of 9 hr.

Both brown dwarfs' effective temperatures in Table \ref{tab:bdProp} are near the condensation temperatures of MgSiO$_3$ and Mg$_2$SiO$_4$ \citep{marley2015rev} so these are viable candidates for clouds in their atmospheres.

\begin{table*}
\begin{center}
\caption{Brown Dwarf Properties}\label{tab:bdProp}
\begin{tabular}{ccccrr}
Name & Rotation Period & Spectral Type & K magnitude  & T$_\mathrm{eff}$ &  $v$ sin($i$) \\
-- & (hr) & -- & -- & (K) & (km/s) \\
\hline \hline
2MASS 1821 & 4.2\tablenotemark{a} & L4 Pec\tablenotemark{b} - L5 Pec\tablenotemark{c} & 11.14 & 1600 $\pm$ 100\tablenotemark{b} & 28.85 $\pm$ 0.16\tablenotemark{d}\\
2MASS 0835 & 3.1\tablenotemark{d} & L4 Pec\tablenotemark{b} - L5 & 11.65 & 1800 $\pm$ 100\tablenotemark{b} & 14.18 $\pm$ 0.43\tablenotemark{d} \\
\end{tabular}
\end{center}
\tablenotetext{a}{\citet{metchev2015weatherII}.}
\tablenotetext{b}{\citet{gagne2015banyan7}.}
\tablenotetext{c}{\citet{looper2008peculiarLdwarfs}}
\tablenotetext{d}{\citet{blake2010nirspecVS}}
\tablenotetext{e}{\citet{koen2004ibandBD}}
\end{table*}

@@

For 2MASS J0835, we observed a simultaneous reference - 2MASS 08354383-0819212, $J$=12.74, $H$=12.28, $K_S$=12.19 at a distance of 28 arcsec.
We obtained spectrophotometry over 4.65 hours, covering about half of a rotation period for 2MASS J0835.

@@

>>>>

The cloud layers may be studied from the direct spectroscopy of a populations of brown dwarf atmospheres \citep[e.g.][]{burgasser2006ltTrans,liu2006}.
Brown dwarfs may be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time \citep[e.g.][]{yang2016exStormsBD}.
In the case where the targets are bright enough for high resolution spectroscopy, Doppler imaging can be used to map out the cloud structures on brown dwarfs \citep{crossfield2014dopplerimg}.

@@

We observed the two brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres.
2MASS J18212815+1414010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
The spectral type is peculiar and has also been designated as L4 \citep{gagne2015banyan7}.
2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L4-L5 brown dwarf known to be variable with a period of 9 hr.
The basic properties of each system are listed in Table \ref{tab:bdProp}.

Both brown dwarfs' effective temperatures in Table \ref{tab:bdProp} are near the condensation temperatures of MgSiO$_3$ (enstatite) and Mg$_2$SiO$_4$ (forsterite) \citep{marley2015rev} so these are viable candidates for clouds in their atmospheres.

\begin{table*}
\begin{center}
\caption{Brown Dwarf Properties}\label{tab:bdProp}
\begin{tabular}{cccccrr}
Name & Rotation Period & Spectral Type & K magnitude  & $J$ - $K$ & T$_\mathrm{eff}$ &  $v$ sin($i$) \\
-- & (hr) & -- & -- & -- & (K) & (km/s) \\
\hline \hline
2MASS 1821 & 4.2\tablenotemark{a} & L4 Pec\tablenotemark{b} - L5 Pec\tablenotemark{c} & 11.14 & 1.78 & 1600 $\pm$ 100\tablenotemark{b} & 28.85 $\pm$ 0.16\tablenotemark{d}\\
2MASS 0835 & 3.1\tablenotemark{e} & L4 Pec\tablenotemark{b} - L5\tablenotemark{f} & 11.65 & 2.03 & 1800 $\pm$ 100\tablenotemark{b} & 14.18 $\pm$ 0.43\tablenotemark{d} \\
\end{tabular}
\end{center}
\tablenotetext{a}{\citet{metchev2015weatherII}.}
\tablenotetext{b}{\citet{gagne2015banyan7}.}
\tablenotetext{c}{\citet{looper2008peculiarLdwarfs}}
\tablenotetext{d}{\citet{blake2010nirspecVS}}
\tablenotetext{e}{Tentative period from \citet{koen2004ibandBD}}
\tablenotetext{f}{\citet{cruz2003coolNeighbors}}
\end{table*}

@@

For 2MASS J0835, we observed a simultaneous reference - 2MASS 08354383-0819212, $J$=12.74, $H$=12.28, $K_S$=12.19 at a distance of 28 arcsec.
We obtained spectrophotometry over 4.65 hours, covering 1.5 rotation periods for 2MASS J0835.

@@

This type of wavelength trend was also recently observed for WISEP J004701.06+680352.1 \citep{lew2016w0047}, which has a much $J-K$ 2.55 spectrum.
In WISEP J0047, the wavelength trend could be fit by $\sim 0.4~\mu$m forsterite grains.
